\tool: A Multi-Mode Attack Model of BadUSB

### 2021-01-13 WOOT/Files/experiment.tex
[experiment] revising case study

\subsubsection{Case study of QR code payment}

\subsection{Attack scenario}

It is worth noting that \tool exposed only a type-c cable (from USB Type-C hub),
and \tool will charge his or her device through this cable, which has no difference from ordinary powerbanks. Noticed the similarity between \tool and normal power bank, we conduct a case study on power bank sharing in order to find out the possibility of \tool being mixed into the circulation of shared power banks.

\subsubsection{Case study of Power Bank Sharing}

@@

>>>>

\subsection{Case study}

We conduct a case study with Power bank sharing and QR code payment as technical background.

\subsubsection{Power bank sharing}

@@

\subsubsection{QR code payment}

\subsubsection{Attack scenario}

It is worth noting that \tool exposed only a type-c cable (from USB Type-C hub),
and \tool will charge his or her device through this cable, which has no difference from ordinary powerbanks. Noticed the low users' vigilance and high similarity between \tool and normal power bank, the attacker can return his/her modified power bank (as \tool) to a power bank station, mixing \tool into the circulation of shared power banks. The next user unconsciously connect his/her device to \tool. 
He/She can find his/her devices being charged as normal.
Like many outdoor mobile phone usage scenarios, the victim may complete payment with showing payment code. In this process, the attacker can preemptively extract and use the victim's payment code to make another payment.
\yechang{tired, go to bed}
